Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-08-05 documents/cpm.tex
the ' typo
figures caption and citation

\graphicspath{{figures/}}

@@

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
the most precise photometric measurements of stars ever made---%
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level so that
it can capture very fine-grained information about the variation of the spacecraft.
The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star. In addition, we use the target star’s future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components), which we set by cross-validation. 
We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5088536-5}
\caption{}
\end{subfigure}%
\hfill
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5949551-5}
\caption{}
\end{subfigure}
\caption{
  \label{ccd} 
  Stars on the same CCD share systematic errors. 
  The two panels show pixel fluxes (brightnesses) for two stars: (a) KIC 5088536, (b) KIC 5949551; 
  here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
  but far enough apart such that there is no stray light from one affecting the other. 
  Each panel shows the pixels contributing to the respective star.
  Note that there exist similar trends in these two stars, caused by systematic errors. 
%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
}
\end{figure}

@@

We also want to emphasis that all the calibration in this paper for \Kepler is 
  based on the assumption that the device is 'self-calibratable', 
  which means all the information we need to calibrate the device are contained in the device itself 
  (either in science data or engineering data) and no external information, 
  for example, measurements from other device, are needed

>>>>

\graphicspath{{figures/png/}}

@@

\begin{abstract}
Astronomical observations are affected by several kinds of noise, each with its own causal source; 
there is photon noise, stochastic source variability, and residuals coming from imperfect calibration of the detector or telescope. 
The precision of NASA \Kepler\ photometry for exoplanet science---% no spaces around ---
the most precise photometric measurements of stars ever made---%
appears to be limited by unknown or untracked variations in spacecraft pointing and temperature, 
and unmodeled stellar variability. Here we present the Causal Pixel Model (\name) for \Kepler\ data, 
a data-driven model intended to capture variability but preserve transit signals. 
The \name\ works at the pixel level so that
it can capture very fine-grained information about the variation of the spacecraft.
The \name\ predicts each target pixel value from a large number of pixels of other stars sharing the instrument variabilities 
while not containing any information on possible transits in the target star. In addition, we use the target star's future and past (auto-regression). 
By appropriately separating, for each data point, the data into training and test sets, 
  we ensure that information about any transit will be perfectly isolated from the model. 
The method has four hyper-parameters (the number of predictor stars, the auto-regressive window size, 
and two L2-regularization amplitudes for model components), which we set by cross-validation. 
We determine a generic set of hyper-parameters that works well for most of the stars and apply the method to a corresponding set of target stars. 
We find that we can consistently outperform (for the purposes of exoplanet detection) 
  the \Kepler\ Pre-search Data Conditioning (PDC) method for exoplanet discovery.

@@

\begin{figure}[htb]
\centering
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5088536-5}
\caption{}
\end{subfigure}%
\hfill
\begin{subfigure}[htb]{0.48\columnwidth}
\includegraphics[width=\columnwidth]{5949551-5}
\caption{}
\end{subfigure}
\caption{
  \label{ccd} 
  Stars on the same CCD share systematic errors. 
  The two panels show pixel fluxes (brightnesses) for two stars in quarter 5: (a) KIC 5088536, (b) KIC 5949551; 
  here, KIC stands for Kepler Input Catalog. Both stars lie on the same CCD, 
  but far enough apart such that there is no stray light from one affecting the other. 
  Each panel shows the pixels contributing to the respective star.
  Note that there exist similar trends in these two stars, caused by systematic errors. 
%The idea of our approach is to predict each pixel from a set of pixels from other stars in order to remove those systematics.
}
\end{figure}

@@

We also want to emphasis that all the calibration in this paper for \Kepler is 
  based on the assumption that the device is 'self-calibratable', 
  which means all the information we need to calibrate the device are contained in the device itself 
  (either in science data or engineering data) and no external information, 
  for example, measurements from other device, are needed.
  And a description of the method in the machine learning context can be found in \cite{icml}
